Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-02-09 manuscript/manuscript.tex
Working on results

>>>>

Of the 6939 records, ChatGPT-4 had the highest PCCC overall and for the adult, child, and neonatal age groups. ChatGPT-3.5 performed better than InterVA-5 and InSilicoVA overall and for the adult and child age groups, but worse than InSilicoVA for the neonatal age group. Figure \ref{fig-perf-agegroup} shows the overall PCCC performance by age group with reference to the CSMF Accuracy.
